---
title: "Brownlows Bets"
author: "Taylor Stohl"
date: "Summer 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)
source(file="BrLw.R")
```


<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

 At the first day of class there are 35 students in Math Statistics class and professor Brownlow always proposes this bet to his students "I will wager $2 to your bet of $1 that at least two people in today's class have  the same birthday.  He tells me he has made that bet 637 times so far. Where do you think his profits are? Discuss this in a markdown document
 
Report git commit structure:
There are 3 questions and there should be at least 3 separate commits, at least one dealing with each of the 3 questions.
1. What are the fair odds for a bet on matching birthdays in a 35 person class.
2. For what size class is a 2:1 odds bet fair.
3. How much money would Brownlow be expected to end up with if the bets went as described.

## Our stategey is to build a Function

The function will be given a class_size, odds, and Number_of_bets made and will give you back how much Brownlows earnings were. We will use it to answer our three questions below.


# What are the fair odds  


<!--Decide on your methods:  In this section explain the approach you will take to attack the issue --- how will you decide on a likely estimate of professor Brownlow's earnings or losses after 637 bets. Also explain how you construct a 95% confidence interval about your estimate of his winnings !-->


We are going to use the BrLw function that we wrote. The function inputs the number of students in a class, the odds that Brownlow is giving, and lastly the number of times Brownlow teaches such a class. 

What comes back out is how much money Brownlow made. 
The function is below



## start with 2.0



```{r}
BrLw(35,2.0,637)
```

These odds are too small, Brownlow keeps making too much money. You can run the same line several times and results are between  the 250 to 350 range. 


```{r}
BrLw(35,3.0,637)
```

These odds are still too much, Brownlow is still making too much money. Results are ranging from about 100 to 180. Getting closer.


```{r}
BrLw(35,4.0,637)
```


```{r}
BrLw(35,4.35,637)
```
Getting closer. it looks like about 4 and some change makes fair odds. 


```{r}
BrLw(35,4.5,637)
```
4.5 seems a little high. 4.35 seems like a good number to go by. Below is a histogram that run the test 100 times with a class size of 35 and and odds of 4.35





```{r}
bank=numeric()
for(j in 1:1000){
  
 
bank[j] = BrLw(35,4.35,637)}
```

```{r}
hist(bank)
```



It looks like the number Brownlow would have to bet for fair odds is somewhere between 4 and 5 
The way to tell by looking at this histogram that the number has reached fair odds is when 0 is in the middle. 




# What size of class makes the 2:1 bet fair?  
<!--Explain and display the results of your method of coming up with the estimate of professor Brownlows betting profits!-->

##  try 34

```{r}
BrLw(34,2,637)
```
To make the bet fair we will test various class sizes. First we will try a class of 34 students. Brownlow is winning too much. 


###  ok try 31



```{r}
BrLw(31,2,637)
```
He is still winning to much money

###  ok try 29


```{r}
BrLw(29,2,637)
```
Still winning more than he is loosing.

###  ok try 28


```{r}
BrLw(28,2,637)
```
Losing more than he is winning. 

The best class size for a fair bet is between 28 and 29 but since we can't only have half a student, 29 is the best choice.

It looks like the earning and losing differentiated. However, the class size where Brownlow appears to be consistently losing is 29.




## We will run the BrLw at the given conditions 1000 times and get a 95% confidence interval


```{r}
bank=numeric()
for(j in 1:1000){
  
 
bank[j] = BrLw(35,2,637)}
```



```{r}
hist(bank)
favstats(bank)
sorted<-sort(bank)
print(sorted[25])
print(sorted[975])
```


Here we have a histogram, second a t.test and lastly a favstats.
The histogram shows the 95% confidence interval
the favstats bases the 95% confidence interval off of the mean minus two times the SD and the mean plus 2 times the SD. 
Every times the code is ran the numbers will change slightly. 


# In the class and payoff as described what is a 95% confidence interval for Brownlow's earnings?
  
<!--Explain and display your method of coming up with a 95% confidence interval of  professor Brownlows winnings (or losings)-->

The 95% confidence interval is created using 25 as its lowest number and 975 as its highest. The 95% confidence interval changes every time the code is ran but it seems to be right around 226 to 340 last time.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If professor Brownlow is consistantly making or losing money how could he change his payout so that his profits center on zero?  Also discuss what size his class should be in order to have his current scheme balance at zero profit.!-->
  
  
It looks like the fair odds for Brownlow was about 4.35 give or take. It definitely between 4 and 5. The way you can determine this is the number is as close to 0 as it can be. 
To make the bet fair the optimal class size is probably 29. Whenever the code is ran, different results are present, and they are sporadic. 
The 95% confidence interval for a class of 35 students changes, but the last time the code was ran it feel between 226 and 340. 

Brownlow is expected to make between about 220 and 340 dollars but just as the code changes, so does the amount of money he is expected to make
